### 2025-04-26 project1/nsSurvey.tex
qwe

\begin{definition}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$, \textcolor{red}{for any $\epsilon > 0$ there exists a $C_\epsilon$ such that}
    $$
         \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C_\epsilon \Gamma^{-\xi} \right) \leq \epsilon.
    $$
\end{definition}

We start our analysis by showing the convergence in probabilistic order from the convergence in \gls{mse}.
Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi} \right)$.
Then, from the definition of convergence in \gls{mse}, there exists a constant $C$ such that 
$$
    \limsup_{\Gamma} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} \leq C.
$$
Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
$$
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-\xi}.
$$
The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail components.
$$
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-\xi}.
$$
The first term is always positive, and the second term can be bounded from below by the indicator function.
\begin{align*}
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
& \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
& = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right).
\end{align*}

Combining bounds on the two terms, we have

$$
    d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-\xi}.
$$

Let $s = -\frac{\xi}{2}$. Arranging the terms, we have

$$
    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{\xi}{2}} \right) \leq \frac{C}{d^2}.
$$

Hence, for all $\epsilon >0$, there exist $C^* = \sqrt{\frac{C}{\epsilon}}$ such that for all $\gamma \geq \Gamma$,

$$
    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{\xi}{2}} \right) \leq \epsilon
$$

In essence, the above expression is a definition of convergence in probabilistic order, that is,

$$
    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{\xi}{2}} \right).
$$

\begin{theorem}\label{thm1:convergence-mse-prob}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
\end{theorem}

Theorem~\ref{thm1:convergence-mse-prob} provides a formal connection between the \textcolor{red}{rate of convergence} in \gls{mse} and that in probabilistic order for \gls{ae} in the context of nested simulation.
It is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.

While the convergence in \gls{mse} implies the convergence in probabilistic order, the converse is not necessarily true.
Similarly, the above argument is applied in reverse.
Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$.
The \gls{mse} of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.

$$
    \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2\xi}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right], 
$$
where the first term can be bounded from above.

\begin{align*}
    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s\}} \right] 
    & \leq d^2 \Gamma^{-2\xi} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
    & = d^2 \Gamma^{-2\xi} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2\xi}.
\end{align*}
However, the second term is not always bounded. 
If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed as follows.

\begin{align*}
    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right] 
    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2\xi}}^{\infty} (x - \rho)^2 f(x) dx.
\end{align*}
Hence, $\hat{\rho}_{\Gamma}$ converges in \gls{mse} to $\rho$ in order $2\xi$ if and only if both integrals converge in order higher than $2\xi$. 
The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in \gls{mse}.
Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in \gls{mse}.
The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the \gls{ae} is not necessarily equivalent to the convergence in \gls{mse}.

>>>>

\begin{definition}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi$ to $\rho$ if for a sufficiently large $\Gamma$, for any $\epsilon > 0$ there exists a $C$ such that
    $$
         \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-\xi} \right) \leq \epsilon.
    $$
\end{definition}

We start our analysis by showing the convergence in probabilistic order from the convergence in \gls{mse}.
\textcolor{red}{Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-\xi-\delta} \right)$ for an arbitrarily small $\delta > 0$.}
\textcolor{red}{Then, from the definition of convergence in \gls{mse}, }
$$
    \limsup_{\Gamma \to \infty} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi-\delta}} \leq C.
$$
\textcolor{red}{for a constant $C > 0$.}

\textcolor{red}{The above inequality implies that}
$$
\limsup_{\Gamma \to \infty} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-\xi}} =0.
$$

\textcolor{red}{Therefore, by Chebyshev's inequality, for any $\epsilon > 0$, we have}
$$
\mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \Gamma^{\xi/2} > C  \right) \leq \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \Gamma^{\xi} \right]}{C^2 } \rightarrow 0 
$$
\textcolor{red}{as $\Gamma \to \infty$.}

\textcolor{red}{Therefore, $\hat{\rho}_{\Gamma}$ converges in probabilistic order $\xi/2$ to $\rho$ as $\Gamma \to \infty$, that is,}
$$
\left| \hat{\rho}_{\Gamma} - \rho \right| = \mathcal{O}_{\mathbb{P}} \left( \Gamma^{-\xi/2} \right).
$$

% Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
% $$
% \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-\xi-\delta}.
% $$
% The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail components.
% $$
% \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-\xi}.
% $$
% The first term is always positive, and the second term can be bounded from below by the indicator function.
% \begin{align*}
% \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
% & \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
% & = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
% & = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right).
% \end{align*}

% Combining bounds on the two terms, we have

% $$
%     d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-\xi}.
% $$

% Let $s = -\frac{\xi}{2}$. Arranging the terms, we have

% $$
%     \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{\xi}{2}} \right) \leq \frac{C}{d^2}.
% $$

% Hence, for all $\epsilon >0$, there exist $C^* = \sqrt{\frac{C}{\epsilon}}$ such that for all $\gamma \geq \Gamma$,

% $$
%     \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{\xi}{2}} \right) \leq \epsilon
% $$

% In essence, the above expression is a definition of convergence in probabilistic order, that is,

% $$
%     \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{\xi}{2}} \right).
% $$

% \begin{theorem}\label{thm1:convergence-mse-prob}
%     Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
%     If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $\xi$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.
% \end{theorem}

% Theorem~\ref{thm1:convergence-mse-prob} provides a formal connection between the \textcolor{red}{rate of convergence} in \gls{mse} and that in probabilistic order for \gls{ae} in the context of nested simulation.
% It is a general result that can be applied to any nested simulation procedure that converges in \gls{mse} to $\rho$ in order $\xi$.
% If the estimator converges in \gls{mse} to $\rho$ in order $\xi$, then it converges in probabilistic order to $\rho$ in order $\frac{\xi}{2}$.

% While the convergence in \gls{mse} implies the convergence in probabilistic order, the converse is not necessarily true.
% Similarly, the above argument is applied in reverse.
% Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-\xi})$.
% The \gls{mse} of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.

% $$
%     \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2\xi}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right], 
% $$
% where the first term can be bounded from above.

% \begin{align*}
%     \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s\}} \right] 
%     & \leq d^2 \Gamma^{-2\xi} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
%     & = d^2 \Gamma^{-2\xi} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2\xi}.
% \end{align*}
% However, the second term is not always bounded. 
% If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed as follows.

% \begin{align*}
%     \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2\xi}\}} \right] 
%     & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2\xi}}^{\infty} (x - \rho)^2 f(x) dx.
% \end{align*}
% Hence, $\hat{\rho}_{\Gamma}$ converges in \gls{mse} to $\rho$ in order $2\xi$ if and only if both integrals converge in order higher than $2\xi$. 
% The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in \gls{mse}.
% Hence, the converse of Theorem~\ref{thm1:convergence-mse-prob} is not necessarily true, and the convergence in probabilistic order is a weaker form of convergence than the convergence in \gls{mse}.
% The immediate implication of this result is that the results in~\cite{wang2022smooth}, which show the convergence in probabilistic order for the \gls{ae} is not necessarily equivalent to the convergence in \gls{mse}.
